\section{Definitions and Basic Notions}

\begin{proposition}
	Let $X$ and $Y$ be topological spaces. Then $\mathcal{B}(X) \otimes \mathcal{B}(Y) \subseteq \mathcal{B}(X \times Y)$. If additionally $X$ and $Y$ are both second countable, then $\mathcal{B}(X\times Y) = \mathcal{B}(X) \otimes \mathcal{B}(Y)$.
\end{proposition}

\begin{proposition}
	Let $(X,\mathcal{A},\mu)$ be a measure space, $(X,\mathcal{A}_\mu,\overline{\mu})$ be its completion and $f: X \to \intcc[0]{-\infty,\infty}$ $\mathcal{A}_\mu$-measurable. Then there exist $\mathcal{A}$-measurable functions $g,h: X \to \intcc[0]{-\infty,\infty}$ with $g \leq f \leq h$ and $g = h$ $\mu$-a.e.
	\label{prop:approx_complete}
\end{proposition}

\begin{proof}
	First assume $f \in \Sigma^+$. Then 
	\begin{equation}
		f = \sum_{i = 1}^n a_i \chi_{A_i}
	\end{equation}

	\noindent where $a_i \leq 0$ and $A_i \in \mathcal{A}_\mu$ for $i = 1,\dots,n$. Since $\mathcal{A}_\mu$ is the completion of $\mathcal{A}$, there exist $E_i,F_i \in \mathcal{A}$ such that 
	\begin{equation}
		E_i \subseteq A_i \subseteq F_i \qquad \text{and} \qquad \mu(F_i \setminus E_i)
	\end{equation}

	\noindent for $i = 1,\dots,n$. Then 
	\begin{equation}
		g := \sum_{i = 1}^n a_i \chi_{E_i} \qquad \text{and} \qquad h := \sum_{i = 1}^n a_i \chi_{F_i}
	\end{equation}

	\noindent have the desired properties.Now let $f$ be a $\mathcal{A}_\mu$-measurable nonnegative function. Then we find a sequence $(\varphi_n)_{n \in \mathbb{N}}$ of $\mathcal{A}_\mu$-measurable simple functions $0 \leq \varphi_n$ such that $\varphi_n \nearrow f$. By the first part we find sequences $(g_n)_{n\in\mathbb{N}}$ and $(h_n)_{n \in \mathbb{N}}$ of $\mathcal{A}$-measurable functions such that 
	\begin{equation}
		g_n \leq \varphi_n \leq h_n \qquad \text{and} \qquad g_n = h_n \>\mu\text{-a.e.}
	\end{equation}

	\noindent for any $n \in \mathbb{N}$. Then clearly 
	\begin{equation}
		\limsup_{n \to \infty} g_n \leq f \leq \liminf_{n \to \infty}h_n
	\end{equation}

	\noindent fulfills the demanded properties. Now let $f$ be an arbitrary $\mathcal{A}_\mu$-measurable function. Then we write 
	\begin{equation}
		f = f^+ - f^-
	\end{equation}

	\noindent where
	\begin{equation}
		f^+(x) := \max(f(x),0) \qquad \text{and} \qquad f^-(x) := \max(-f(x),0)
	\end{equation}

	\noindent for $x \in X$. Then by the preceeding part there exist $\mathcal{A}$-measurable functions
	\begin{equation}
		g^+ \leq f^+ \leq h^+ \qquad \text{and} \qquad g^- \leq f^- \leq h^-
	\end{equation}

	\noindent such that $g^+ = h^+$ and $g^- = h^-$ holds $\mu$-a.e. Then 
	\begin{equation}
		g^+ - h^- \leq f \leq h^+ - g^-
	\end{equation}

	\noindent fulfills the desired properties.
\end{proof}

\begin{corollary}
	Let $f: \mathbb{R}^n \to \intcc[0]{-\infty,\infty}$ be $\mathcal{M}_{\lambda^*}$-measurable. Then there exists a $\mathcal{B}(\mathbb{R}^n)$-measurable function $g$, such that $f = g$ $\lambda$-a.e.
\end{corollary}

\begin{proof}
	This immediately follows by proposition \ref{prop:approx_complete} since the Lebesgue measure on $(\mathbb{R}^n,\mathcal{M}_{\lambda^*})$ is the completion of Lebesgue measure on $(\mathbb{R}^n,\mathcal{B}(\mathbb{R}^n))$.
\end{proof}

\section*{Exercises}

\begin{exercise}
	Let $X$ be a set. Determine $\sigma(\cbr[0]{\cbr[0]{x} : x \in X})$.
\end{exercise}

\begin{exercise}
	Let $X,Y$ be sets, $A \subseteq \mathcal{P}(Y)$ and $f: X \to Y$ be surjective. Then 
	\begin{equation}
		m\del[0]{\cbr[0]{f^{-1}(S) : S \in A}} = \cbr[0]{f^{-1}(S) : S \in m(A)}.
	\end{equation}

	\textit{Hint:} For the inclusion $\supseteq$ consider the set 
	\begin{equation}
		\mathcal{M} := \cbr[0]{B \subseteq Y : B \in m(A) \text{ and } f^{-1}(B) \in m\del[0]{\cbr[0]{f^{-1}(S) : S \in A}}}.
	\end{equation}
\end{exercise}

\begin{exercise}
	Show that there is no countable $\sigma$-algebra.
\end{exercise}

\begin{exercise}
	
\end{exercise}
